Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
revise II. paragraph 1

Unfortunately, the field of signal-based eco-acoustics is still in infancy.
As a consequence, very few well built datasets are readily available for evaluation purposes.
A closely related field of investigation, which is relatively more mature, is the classification of acoustic scenes whose aim is to predict labels by processing audio data.
Despite being narrower in terms of range of applications, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data mining community for a while, with availability of a few well-designed datasets.

@@

As stated in the introduction, the field of eco-acoustics is relatively young, but significant works are worth mentioning. One avenue of research issued from bio acoustic studies, consider the audio stream as a set of events produced animals, and is processed to retrieve the precise species that produced the sound and potentially the type of vocalization in order to predict some behavior of the animal under study \cite{au2008principles, stowell2014large}. Another, more recent, avenue of research, tackles problems associated with long duration recordings of the environment, in particular, building recognizers for species of interest, extracting acoustic indices to aid navigation and visualisation. It typically process the audio stream in an holistic manner in order to infer large time-scale properties of the bio-acoustic scene for example to estimate which part of the stream need to be analyzed more in details, \textit{i.e.} by a human \cite{rosenstock2002landbird,diefenbach2007incorporating}.

>>>>

Unfortunately, the field of signal-based ecoacoustics is still in infancy.
As a consequence, very few well built datasets are readily available for evaluation purposes.
A closely related field of investigation, which is relatively more mature, is the classification of acoustic scenes whose aim is to predict labels by processing audio data.
Despite being narrower in terms of range of applications, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data mining community for a while, with availability of a few well-designed datasets.

@@

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices, migration patterns, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.
